Can BERT learn dialogue-specific phenomena? The case of laughter in dialogue act recognition.

### 2020-07-20 reports/Star-SEM Paper/starsem-paper.tex
add results discussion

\title{Can BERT learn dialogue specific phenomena? The case of laughter in dialogue act recognition. }

@@

@@

Next, we assess the effect of further in-domain pre-training on BERT's performance as an utterance encoder.\footnote{
In-domain pre-training is sometimes referred to as \textit{fine-tuning}, but we reserve that term for task-specific training on labeled data.}
We construct pre-training corpora from the SWDA portion of the un-labeled Switchboard corpus and from the entire AMI corpus (including the 32 dialogues with no human-annotated DA tags that are not included in the DAR training set).
In both cases, we exclude dialogues that are reserved for DAR testing.

the in-domain corpus (\texttt{BERT+ID}) and the combined corpus (\texttt{BERT+CC}).

We use the same pre-training task described by \citet{devlinBERTPretrainingDeep2018}, which combines masked token prediction and next sentence (utterance) detection. 
Distractor utterances are drawn at random from another dialogue in the corpus
and each epoch is generated separately so that different distractor sentences appear each time.
We pre-trained three BERT models: with Switchboard (10 epochs), AMI (10 epochs), and the combined corpus (5 epochs).

For each dialogue act corpus, we trained DAR models with BERT encoders that received additional pre-training on the three different pre-training corpora. 
As before, we experimented with both the fine-tuning and frozen conditions.

The results are mixed.
In-domain pre-training offers a modest boost in overall accuracy,
but the macro-average scores are almost uniformly worse (Table~\ref{table:exp3}).
%Indeed, when BERT is frozen during fine-tuning, the model that received no further pre-training performs better by more than 3 percentage points (Table~\ref{tab:exp3-recall}).
To fully assess the potential impact of further in-domain pre-training, a larger dialogue corpus is required.

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
\begin{tabular}{@{}lrrrr@{}}
\toprule
           & \multicolumn{2}{c}{SWDA}                          & \multicolumn{2}{c}{AMI-DA}                        \\ \midrule
           & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} \\
\texttt{BERT-FT}    & 45.99                  & 76.93                    & 50.03                  & 66.95                    \\
\texttt{BERT+ID-FT} & 45.48                  & 77.02                    & 46.56                  & 68.66                    \\
\texttt{BERT+CC-FT} & 47.78                  & 77.35                    & 48.72                  & 66.58                    \\ \midrule
\texttt{BERT-FZ}    & 7.75                   & 55.61                    & 14.44                  & 46.60                    \\
\texttt{BERT+ID-FZ} & 6.46                   & 52.30                    & 14.43                  & 48.07                    \\
\texttt{BERT+CC-FZ} & 5.76                   & 51.14                    & 12.56                  & 42.42                    \\ \bottomrule
\end{tabular}
  \caption{Comparison of macro-average F1 and accuracy  with further in-domain (\texttt{ID}) and combined corpus (\texttt{CC}) dialogue pre-training,
    for both the frozen (\texttt{FZ}) and fine-tuned (\texttt{FT}) conditions.}
  \label{table:exp3}
\end{table}

>>>>

\title{Can BERT learn dialogue-specific phenomena? The case of laughter in dialogue act recognition. }

@@

\subsection{Pre-training corpora}

We also experiment with three unlabeled dialogue corpora, which we use to provide further pre-training for the BERT encoder.

The first two corpora are constructed from the same source as the dialogue act corpora.
We use the SWDA portion of the un-labeled Switchboard corpus (SWBD) and the entire AMI corpus (including the 32 dialogues with no human-annotated DA tags that are not included in the DAR training set).
In both cases, we exclude dialogues that are reserved for DAR testing.

We also experiment with a much larger a corpus constructed from OpenSubtitles \citep{Lison2016}.
We used a manually constructed list of words frequenty used to refer to laughter in subtitles and replaced every occurance of one of these words with the special laughter token. 
Then, we collected every English-language subtitle file in which at least 1\% of the utterances contained laughter (about 11\% of the total).
Because utterances are not labeled with speaker in the OpenSubtitles corpus, we randomly assigned a speaker token to each utterance to maintain the format of the other dialouge corpora.

The pre-training corpora were prepared for the combined maksed language modeling and next sentence (utterance) prediction task, as described dy \citet{devlinBERTPretrainingDeep2018}.
For the smaller SWBD and AMI corpora, we generate and train on multiple epochs of data. Since there is randomness in the data preparation (e.g., which distrcactor sentences are chosen and which tokens are masked), we generate each training epoch separately.\footnote{Also see the Hugging Face \href{https://github.com/huggingface/transformers/tree/1.1.0/examples/lm_finetuning}{finetuning example}.}

\begin{table}[ht]
\centering
\begin{tabular}{@{}llll@{}}
\toprule
       & tokens & \% laughs & epochs\\ \midrule
AMI           & 1M     & 1.3             & 10     \\
SWBD          & 1.5M   & 0.5             & 10     \\
OpenSubtitles & 350M   & 0.3             & 1      \\ \bottomrule
\end{tabular}
\caption{Pre-training corpora, showing laughter representation as a percentage of total tokens and number of pre-training epochs generated.}\label{tab:pretraining-corpora}
\end{table}

@@

Next, we assess the effect of additional dialogue pre-training on BERT's performance as an utterance encoder.\footnote{
In-domain pre-training is sometimes referred to as \textit{fine-tuning}, but we reserve that term for task-specific training on labeled data.}
\citet{sunHowFineTuneBERT2019} has reported that performing additional pre-training on unlabeled in-domain data improves performance on classification tasks. 
We want to see if BERT can bennefit from pre-training, on dialogue data, including from data outside the immediate target domain.

For each of the target corpora (SWDA and AMI-DA), we compare four different pre-training conditions: 
The in-domain corpus (\texttt{ID}), consisting of the AMI pre-training corpus for the AMI-DA model and the SWBD pre-traning corpus for the SWDA model; 
the cross-domain corpus (\texttt{CC}), consisting of both the AMI and SWBD pre-training corpora; 
the OpenSubtitles corpus (\texttt{OS});
and finally the standard BERT\textsubscript{BASE} model with no addational pre-training.
As before, we experiment with both frozen and fine-tuned models at the task training stage.

We performed 10 epochs of pre-training on the in-domain models and 5 epochs of pre-training on the cross-domain models so that the total amount of training data was comparable. The OpenSubtitles models trained on much more data (see Table~\ref{tab:pretraining-corpora}) and were trained for only one epoch.

In the fine-tuned condition, additional pre-training offers a modest boost in overall accuracy and a substantial boost to the macro-average scores.
Any of the dialogue corpora appear helpful, but the cross-domain corpus generally provides the largest boost.
In the frozen condition, only the very large OpenSubtitles corpus is helpful, suggesting that when adapting BERT to dialogue, the size of the corpus is more important than its quality or fidelity to the target domain.
Still, pre-training provides nowhere near the performance improvement achieved by fine-tuning on the target task.

\begin{table}[]
\begin{tabular}{@{}lrrrr@{}}
\toprule
           & \multicolumn{2}{c}{SWDA}                          & \multicolumn{2}{c}{AMI-DA}                        \\ \midrule
           & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} \\
\texttt{BERT-FT}    & 36.75                  & 76.60                    & 43.42                  & 64.93                    \\
\texttt{BERT+ID-FT} & 43.63                  & 77.01                    & 46.70                  & \textbf{68.88}           \\
\texttt{BERT+CC-FT} & \textbf{47.78}         & \textbf{77.35}           & \textbf{48.86}         & 68.79                    \\ 
\texttt{BERT+OS-FT} & 41.42                  & 76.95                    & 48.65                  & 68.07                    \\ \midrule
\texttt{BERT-FZ}    &  7.75                  & 55.61           & 14.86                  & 48.34                    \\
\texttt{BERT+ID-FZ} &  6.46                  & 52.30                    & 14.48                  & 48.18                    \\
\texttt{BERT+CC-FZ} &  5.76                  & 51.14                    & 11.34                  & 40.48                    \\ 
\texttt{BERT+OS-FZ} &  \textbf{9.60}         & \textbf{57.67}           & \textbf{17.03}         & \textbf{51.03}           \\ \bottomrule
\end{tabular}
  \caption{Comparison of macro-average F1 and accuracy  with further in-domain (\texttt{ID}) and combined corpus (\texttt{CC}) dialogue pre-training,
    for both the frozen (\texttt{FZ}) and fine-tuned (\texttt{FT}) conditions.}
  \label{table:exp3}
\end{table}
